\documentclass[a4paper]{article}

\usepackage[margin=1.5cm]{geometry}
\usepackage[T1]{fontenc}  % Replace fontspec
\usepackage{times}        % Times New Roman font
\usepackage[svgnames]{xcolor}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}
\usepackage{calc}
\usepackage{ragged2e}
\usepackage{etoolbox}
\usepackage{xparse} 

\hypersetup{
    pdftitle={Resume - Dean Masley},
    pdfauthor={Dean Masley},
    pdfsubject={Frontend developer \& Design},
    pdfkeywords={frontend developer, design},
    pdfcreator={LaTeX},
    pdfproducer={pdfTeX}
}

% -----------------------------
% Design Tokens
% -----------------------------

% Colors (using Apple's SF palette as inspiration)
\definecolor{textPrimary}{HTML}{000000}     % Label Color (Primary)
\definecolor{textSecondary}{HTML}{3C3C3C}   % Label Color (Secondary)
\definecolor{textTertiary}{HTML}{6C6C6C}    % Label Color (Tertiary)
\definecolor{divider}{HTML}{E5E5E5}         % Separator Color
\definecolor{linkColor}{HTML}{0366D6}       % GitHub-style blue for links

\hypersetup{
    colorlinks=true,
    urlcolor=linkColor,
    linkcolor=linkColor
}

% Base unit for consistent spacing (1pt = 1/72.27 inch)
\newlength{\baseunit}
\setlength{\baseunit}{8pt}  % Base spacing unit

% Spacing scale
\newcommand{\spacingxxs}{\vspace{0.25\baseunit}}  % 2pt
\newcommand{\spacingxs}{\vspace{0.5\baseunit}}    % 4pt
\newcommand{\spacingsm}{\vspace{\baseunit}}       % 8pt
\newcommand{\spacingmd}{\vspace{2\baseunit}}      % 16pt
\newcommand{\spacinglg}{\vspace{3\baseunit}}      % 24pt
\newcommand{\spacingxl}{\vspace{4\baseunit}}      % 32pt
\newcommand{\companySpace}{\vspace{1.25\baseunit}}
\newcommand{\subtitleSpace}{\vspace{-1.25\baseunit}}
\newcommand{\roleSpace}{\vspace{0.75\baseunit}}

% -----------------------------
% Typography System
% -----------------------------

% Typography commands
\newcommand{\displayOne}[1]{{\Large\fontsize{16}{16}\selectfont #1}}    % Large Title
\newcommand{\displayTwo}[1]{{\Large\fontsize{16}{16}\selectfont #1}}    % Title 1
\newcommand{\headingOne}[1]{{\large\fontsize{14}{14}\selectfont #1}}    % Title 2
\newcommand{\headingTwo}[1]{{\normalsize\fontsize{12}{12}\selectfont #1}}    % Title 3
\newcommand{\headingThree}[1]{{\fontsize{8}{8}\bfseries\selectfont #1}}       % Headline
\newcommand{\bodyLarge}[1]{{\fontsize{9}{9}\selectfont #1}}                   % Body Large
\newcommand{\bodyDefault}[1]{{\fontsize{8}{8}\selectfont #1}}                 % Body
\newcommand{\bodySmall}[1]{{\fontsize{8}{8}\selectfont #1}}                   % Footnote
% -----------------------------
% Layout Configuration
% -----------------------------

\setlength{\parindent}{0pt}
\setlength{\parskip}{\baseunit}
\linespread{1.1}
\renewcommand{\arraystretch}{1.15}

% -----------------------------
% Component Styles
% -----------------------------

\newcommand{\summary}[1]{%
    {\bodyDefault{\setlength{\parskip}{0.5\baseunit}%
    \setlength{\baselineskip}{1.4\baseunit}%
    #1}}%
    \spacingxs
}

\newcommand{\company}[3][]{%
    {\headingThree{\textcolor{textPrimary}{#2}}}%
    \hfill{\bodySmall{\textcolor{textTertiary}{#3}}}\par
    \ifx\relax#1\relax\else
        \subtitleSpace
        {\bodySmall{\textcolor{textTertiary}{#1}}}
    \fi
    \vspace{-0.75\baseunit}}

\newcommand{\resumeHeader}[3]{%
    \begin{minipage}[c]{0.5\textwidth}
        {\displayOne{\textcolor{textPrimary}{#1}}}\\
        {\bodyLarge{\textcolor{textSecondary}{#2}}}%
    \end{minipage}%
    \hfill
    \begin{minipage}[c]{0.5\textwidth}
        \raggedleft
        {\bodySmall{#3}}%
    \end{minipage}
}

\newcommand{\customDivider}{%
    \spacingsm
    {\color{divider}\hrule height 0.5pt}%
    \spacingsm
}

\newcommand{\sectionHeading}[1]{%
    \customDivider
    {\headingTwo{\textcolor{textPrimary}{#1}}}%
    \spacingxxs
}

\newenvironment{customItemize}{%
    \begin{itemize}[
        leftmargin=1.5\baseunit,
        itemsep=0\baseunit,
        parsep=0pt,
        topsep=0\baseunit,
        label={\textcolor{textPrimary}{\small\textbullet}}]%
}{%
    \end{itemize}}

\NewDocumentCommand{\role}{m m m o}{%
    {\bodyDefault{\textcolor{textSecondary}{\textit{#1}}}}%
    \hfill{\bodySmall{\textcolor{textTertiary}{\textit{#2 -- #3}}}}%
    \IfValueT{#4}{%
        \\\bodySmall{\textcolor{textTertiary}{#4}}%
    }%
    \vspace{-0.75\baseunit}%
}

\NewDocumentCommand{\achievement}{o m o}{%
    \item {\bodyDefault{#2}}%
    \IfValueT{#1}{%
        \space{\bodySmall{\textcolor{textTertiary}{[#1]}}}%
    }%
    \IfValueT{#3}{%
        \\\bodySmall{\textcolor{textTertiary}{Impact: #3}}%
    }%
}

\newcommand{\skillBlock}[2]{%
    \begin{minipage}[t]{0.31\textwidth}
        {\bodyDefault{\textbf{\textcolor{textPrimary}{#1}}}}\par
        \spacingxxs
        {\bodyDefault{#2}}%
    \end{minipage}}



\newcommand{\education}[5]{
    % #1: Degree | #2: Institution | #3: Duration | #4: Location | #5: Specialization/Minor (optional)
    {\bodyDefault{\textbf{#1}}}
    \if\relax\detokenize{#5}\relax\else
        \vspace{-0.25\baseunit}
        {\bodySmall{\textcolor{textTertiary}{ -- #5}}}
    \fi
    \hfill
    {\bodySmall{\textcolor{textTertiary}{#3}}}\\
    {\bodyDefault{\textcolor{textTertiary}{#2}}} \hfill {\bodySmall{\textcolor{textTertiary}{#4}}}

}

\newcommand{\coursework}[1]{
    \vspace{0.25em}
    \begin{customItemize} #1 \end{customItemize}
}

% New command for notable projects
\newcommand{\project}[2][]{
    % #1: Tech stack (optional) | #2: Project description
    \item #2
    \if\relax\detokenize{#1}\relax\else
        {\textcolor{textTertiary}{\textit{[#1]}}}
    \fi
}

\newcommand{\engagement}[3]{
    \item \bodyDefault{#1} \hfill \bodySmall{\textcolor{textTertiary}{
        \if\relax\detokenize{#2}\relax\else #2, \fi #3}}

}

\newcommand{\award}[3]{
    \item \bodyDefault{#1} \hfill \bodySmall{\textcolor{textTertiary}{
        \if\relax\detokenize{#2}\relax\else #2, \fi #3}}
}

% -----------------------------
% Start Document
% -----------------------------

\pagestyle{empty}
\color{textPrimary}
% Add before \begin{document}
\raggedbottom  % Prevents awkward vertical stretching
\widowpenalty=10000
\clubpenalty=10000
\brokenpenalty=10000

% Better table spacing control
\setlength{\tabcolsep}{6pt}
\renewcommand{\arraystretch}{1}

\raggedbottom

\begin{document}

\resumeHeader{Dean Masley}{Frontend Developer, Design (2d \& 3d) \& Biz-Dev}{
    \href{mailto:dean@dean.lol}{\textcolor{textTertiary}{dean@dean.lol}} \\[0.15\baseunit]
    \href{tel:+31640490432}{\textcolor{textTertiary}{+31 6 40490432}} \\[0.15\baseunit]
    \href{https://github.com/jollygrin}{\textcolor{linkColor}{GitHub}} \textbullet{}
    \href{https://linkedin.com/in/dmasley}{\textcolor{linkColor}{LinkedIn}} \\[0.15\baseunit]
    \href{https://cv.dean.lol}{\textcolor{linkColor}{cv.dean.lol}} \\[0.15\baseunit]
}

\sectionHeading{Professional Summary}

\summary{Dynamic entrepreneur with a proven track record of cofounding impactful ventures and evolving into a multifaceted professional with expertise in business development, design, and frontend development. Starting with leadership roles in international nonprofits and startups, I honed skills in creating compelling narratives, strategic partnerships, and innovative products. Transitioning to tech, I mastered frontend development over five years, building complex platforms in the financial planning, insurance, and pension sectors. Outside of work, I push creative and technical boundaries through side projects, such as developing a metaverse club (3d design, code, attendance tracking systems, ethereum OAuth, NFT bulk distributions, organizing artists from across the world, 2+ years of shows every month) and boardgame simulators that can be played online with friends. Passionate about leveraging technology and design to turn ambitious (or just fun) ideas into reality.}

\spacingsm
% \sectionHeading{Technical Expertise}

\customDivider
\begin{tabular}{@{}p{0.23\textwidth}@{\hspace{0.02\textwidth}}p{0.23\textwidth}@{\hspace{0.02\textwidth}}p{0.23\textwidth}@{\hspace{0.02\textwidth}}p{0.23\textwidth}@{}}
    \skillBlock{Design}{
        Figma \\
        Blender (3d modeling) \\
        Davinci Resolve (Video editing) \\
    } &
    \skillBlock{Frontend Frameworks}{
        Next.js / React \\
        Svelte(kit) \\
        Angular \\
        Decentraland SDK
    } &
    \skillBlock{Proficient}{
        React-query (tanstack) \\
        Tailwind / Chakra / Vanilla CSS \\
        Three.js \\
        Eth/Solana Dapps
    } &
    \skillBlock{ }{
        Unit testing (jest) \\
        Browser automation / E2E (pupeteer/cyprus) \\
        OAuth2.0 \& API Security \\
        Websockets
    }
\end{tabular}


\spacingsm
\sectionHeading{Professional Experience}

\company[Compliant pension \& insurance ecosystem infrastructure]{Hyfen}{Amsterdam, Netherlands}

\role{Frontend Engineer}{2020}{2024}
\begin{customItemize}
    \achievement[Authorization]{Integrated Azure (MSAL) for secure and compliant login authorization.}
    \achievement[Code Quality]{Delivered high-quality code with >80\% unit test coverage, ensuring reliability through refactoring.}
    \achievement[API Handling]{Implemented robust API handling, including caching, token management, file uploads, and error handling.}
    \achievement[Typesafety]{Developed custom tooling to generate type files, streamlining frontend-backend collaboration.}
    \achievement[Style Systems]{Built reusable style systems for consistent, design-accurate UI across projects.}
    \achievement[Client/Server]{Worked on client- and server-rendered components, resolving hydration errors and enhancing security.}
    \achievement[Collaboration]{Collaborated with cross-functional teams to align business requirements, design, and backend workflows.}
\end{customItemize}

\company[Crowdfund sustainable energy and reduce your energy bill]{NestEgg}{Heerlen, Netherlands}

\role{Co-Founder}{2017}{2019}
\begin{customItemize}
    \achievement[Startup Launch]{Co-founded and launched a platform for sustainable energy crowdfunding, securing investment and partnerships with major Dutch institutions.}
    \achievement[UX Design]{Designed intuitive user experiences, enabling rapid prototyping and seamless implementation of core features.}
    \achievement[Product Delivery]{Led the end-to-end process from ideation to launch, allowing users to crowdfund projects and reduce energy bills.}
\end{customItemize}

\company[International nonprofit empowering students to launch blockchain clubs]{Blockchain Education Network}{Global}

\role{Executive Director}{2015}{2017}
\begin{customItemize}
    \achievement[Global Growth]{Expanded the network to over 200 student-led blockchain clubs across North America, Europe, and Asia.}
    \achievement[Decentralized Leadership]{Adopted a swarmwise organizational model, empowering local leaders to scale independently.}
    \achievement[Advocacy]{Delivered high-profile speeches, including TED Talks and international summits, to promote blockchain education.}
    \achievement[Fundraising]{Raised over \$125k in donations to support organizational growth and global events.}
    \achievement[Team Leadership]{Managed an 8-member executive team to oversee outreach, events, and administrative operations.}
    \achievement[Branding]{Revitalized branding with a new logo, website, and marketing materials, positioning the organization for growth.}
\end{customItemize}


\spacingxl
\spacingxl

\sectionHeading{Passion Projects}

\company[Play the card game Sorcery TCG online in the browser | ~1100 users/mo]{Spells Bar}{spells.bar}

\role{Creator}{2024}{Present}
\begin{customItemize}
    \achievement[Inspiration]{Identified a gap for an accessible way to play Sorcery TCG online and created a solution.}
    \achievement[Websockets]{Implemented multiplayer functionality using websockets, enabling lobby creation and real-time gameplay.}
    \achievement[CSS Grid]{Designed a complex CSS Grid system to manage and display 36+ card slots dynamically.}
    \achievement[Drag-and-Drop]{Developed smooth drag-and-drop interactions for intuitive card placement in designated zones.}
    \achievement[User-Centric Iteration]{Rapidly improved the platform based on user feedback, addressing pain points to ensure stability.}
    \achievement[Sustainability]{Built a static site hosted on GitHub Pages, with a lightweight and easily swappable server backend.}
\end{customItemize}

\company[Metaverse club streaming live artists from around the globe | ~400 users/mo]{Innkeeper}{Decentraland}

\role{Creator}{2021}{Present}
\begin{customItemize}
    \achievement[Dynamic Venues]{Designed and modeled 3D venues in Blender, updating regularly to keep the experience fresh.}
    \achievement[Creative Rewards]{Produced weekly 3D cover art and distributed 22+ months of free music NFTs to attendees as rewards.}
    \achievement[Ethereum Integration]{Secured land ownership and safely managed deployments using Ethereum CLI tools.}
    \achievement[Custom Features]{Built metaverse functionality, including attendance tracking, VIP zones, dynamic banners, and interactive elements with Decentraland SDK.}
    \achievement[Artist Network]{Curated and grew a roster of 100+ artists, hosting weekly live performances from around the world.}
    \achievement[Data Management]{Developed a PostgreSQL database to manage attendance, artist records, payments, and event scheduling.}
    \achievement[Music NFTs]{Led the creation and automation of music NFT distributions, using scripts to streamline bulk blockchain transactions on Polygon.}
    \achievement[Grant Recognition]{Secured grant funding to pay artists for six months, providing consistent, paid opportunities for performers.}
\end{customItemize}

\company[Play the board game Unmatched online in the browser | ~350 users/mo]{Unbrewed}{unbrewed.xyz}

\role{Creator}{2020}{Present}
\begin{customItemize}
    \achievement[Inspiration]{Created an open-source browser-based version of Unmatched during COVID, offering a free alternative to a paid desktop app.}
    \achievement[Partnership]{Gained permission from the board game's creators to build a noncommercial, open-source simulator.}
    \achievement[Real-Time Gameplay]{Built a GO backend with websockets and a Next.js frontend to enable multiplayer games with persistence.}
    \achievement[Interactive Board]{Leveraged the Canvas API to create drag-and-drop functionality for real-time token movements.}
    \achievement[User-Centric Iteration]{Improved the platform iteratively based on user feedback, enhancing performance and usability.}
    \achievement[Longevity]{Refactored the app for static generation and hosted on GitHub Pages, with an easily deployable backend to ensure future maintainability.}
\end{customItemize}



\spacingsm


% ------------------ Education ------------------ %
\sectionHeading{Education}

\education{Bachelor Marketing}{University of Delaware}{2012 -- 2016}{Delaware, USA}{Minor in German}

\spacingsm

% ------------------ Coursework ------------------ %

% ------------------ Projects ------------------ %

% ------------------ Speaking Engagements ------------------ %
\sectionHeading{Speaking Engagements and Recognitions}

\begin{minipage}[t]{0.55\textwidth}
    \begin{customItemize}
        \engagement{Keynote 2016 (Blockchain) -- Keynote Speaker}{}{Burj al Arab Dubai, June 2016}
        \engagement{TEDxYouth -- Presenter}{}{Sittard, 2017}
        \engagement{North American Bitcoin Conference -- Presenter}{}{Miami, 2017}
        \engagement{Internet of Agreements (Space) -- Presenter}{}{London, 2018}
    \end{customItemize}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.40\textwidth}
    \begin{customItemize}
        \award{Track 1st Place - Dutch Blockchain Hackaton}{}{2017}
        \award{Track 2nd Place - Blockchain'gers Hackathon}{}{2019}
        \award{GitHub Arctic Code Vault Contributor}{}{2020}
    \end{customItemize}
\end{minipage}

\end{document}
